Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-02-12 Submission.tex
Updated methods section.

\abstract{
Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demanding. We build on a small but growing literature suggesting that individual differences may matter. The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics. O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource. The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability. Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
}

@@

The integration of the literature above results in two primary predictions. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (M. A. LePine, 2022). M. A. LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

@@

\begin{quote}
Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand.
\end{quote}

We explore three research questions addressing whether our literature-implicated job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).

@@

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource, challenge, or hindrance for that characteristic. For characteristics that \emph{were} implicated as being relevent for their job, they were then asked to report how much a characteristic was a resource, and then how much each characteristic was a hindrance, and finally, how much each item was a challenge. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

The Occupational Information Network (O*NET; onetonline.org) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. We used 98 statements taken from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}. We retained 41 work activity classifications which O*NET groups into categories of information input (5 statements; Where and how are the information and data gained that are needed to perform this job?), interacting with others (17 statements; What interactions with other persons or supervisory activities occur while performing this job?), mental processes (10 statements; What processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (9 statements; What physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Fifty-seven work context statements grouped into interpersonal relationships (14 statements; This category describes the context of the job in terms of human interaction processes), physical work conditions (30 statements; This category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (13 statements; This category involves the relationships or interactions between the worker and the structural characteristics of the job).

These descriptors often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, the statement ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the statement, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. The O*Net descriptors are written in a similar manner to a task statement presented within a job analysis, but the level of abstraction is closer to ``responsibility'' than task. For example, the descriptor for ``level of competition,'' which is an element of the ``structural job characteristics'' grouping, is \emph{\ldots to what extent does this job require the worker to compete or to be aware of competitive pressures?} Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we retained the O*Net wording for our item stems. We also retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales.

We retained the essence of each O*NET descriptor to capture characteristics of relevance for each respondent. Subsequent to these self evaluations, each respondent who agreed that the element had \emph{at least some relevance} to their job was also asked to rate that element in terms of, 1) \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development, 2) \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains, and 3) \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment.

@@

@@

The first prediction asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource. Figure \ref{fig:overallhist} presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).

@@

The second prediction stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

In addition to the two predictions, three related research questions were proposed. To answer these research questions, authors first categorized items into the categories listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?'' Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. ADD ANOVAS HERE - one way repeated measures for each category (total of 10 analyses). describe pattern. In sum, these results provide \_\_\_ support for RQ 1 and 2.

see Figure \ref{fig:scalelevelgraphs}

@@

\hypertarget{literature-implicated-demands}{%
\subsection{Literature-implicated demands}\label{literature-implicated-demands}}

@@

\hypertarget{literature-implicated-resources}{%
\subsection{Literature-implicated resources}\label{literature-implicated-resources}}

@@

The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net. The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors. This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1. Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are. Lastly, we also found support for the prediction that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).

\hypertarget{implications}{%
\section{Implications}\label{implications}}

@@

\hypertarget{limitations-and-future-directions}{%
\section{Limitations and Future Directions}\label{limitations-and-future-directions}}

As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here. First, we captured only a small number of job characteristics given the nature of our research questions. Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include. Related to that, we intentionally worked within the O\emph{Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands. For example, we included minimal ``social'' resources or interactions with one's supervisor, which the literature would suggest are important resources. Future study should explore this aspect of work. We also used the exact definitions of resource, challenge, and hindrance. It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently. It would also be interesting to consider outcomes associated with subjective ratings.
Lastly, there may be some practical utility to pursue training interventions aimed at }how* characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.{[}\^{}check{]} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.

>>>>

\abstract{
Much of our understanding of job demands and resources rests on the assumption that some aspects and components of one's job are resources and some are demands. We build on a small but growing literature suggesting that individual differences may matter our perception of characteristics as demands and resources. The primary aims were to explore 1) whether there is variability in subjective ratings of job characteristics with respect to how much they served as resources and demands, and 2) whether or not there was a match between the literature-implicated resources/demands and subjective ratings of these characteristics. O*NET work characteristics were rated by 568 employed respondents in terms of relevance, perception as a demand, and perception as a resource. The results suggest that job characteristics differ in variability/stability regarding subjective worker perceptions, particularly for hindrance demands which showed the most variability. Job characteristics were not uniquely categorized as a resource or demand as evidenced by correlations, and lastly, literature-implicated resources not consistently rated as job resources or demands.
}

@@

The integration of the literature above results in two primary hypotheses. The first addresses whether employees generally agree on their appraisals of job characteristics as resources or challenge or hindrance demands. For instance, although challenge stressors tend to be appraised more so as challenges, and hindrance stressors tend to be appraised more as hindrances than challenges, others have reported variability in these appraisals (M. A. LePine, 2022). M. A. LePine (2022), in fact, argues that the challenge-hindrance stressor framework acknowledges that these appraisals are not universal. Thus, it is quite possible, given the theoretical and empirical evidence presented above, that there is wide variability in individual appraisal of work activities and context such that some people may rate a given activity as a resource and others a hindrance.

@@

\begin{quote}
Hypothesis 2: Job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are viewed as both a resource and a demand.
\end{quote}

Two exploratory questions further address whether our \emph{literature-implicated} job characteristics (e.g., autonomy) are consistently rated as our research models suggest across the job-demands resources theory (Bakker \& Demerouti, 2017) and challenge-hindrance stressor framework (Cavanaugh et al., 2000).

@@

@@

The Occupational Information Network (O*NET) contains a comprehensive description of occupations (Peterson et al., 2001). This widely accessed database houses hundreds of standardized and occupation-specific descriptors most occupations in the US and these descriptions are continually updated. We used 98 statements/questions from O*NET \href{https://www.ONETonline.org/find/descriptor/result/4.A.1.b.3}{activity and context classifications}. We retained work activity classifications which O*NET groups into categories of information input (e.g., where and how are the information and data gained that are needed to perform this job?), interacting with others (e.g., what interactions with other persons or supervisory activities occur while performing this job?), mental processes (e.g., what processing, planning, problem-solving, decision-making, and innovating activities are performed with job-relevant information?) and work output (e.g., what physical activities are performed, what equipment and vehicles are operated/controlled, and what complex/technical activities are accomplished as job outputs?). Work context statements were grouped into interpersonal relationships (i.e., this category describes the context of the job in terms of human interaction processes), physical work conditions (i.e., this category describes the work context as it relates to the interactions between the worker and the physical job environment), and structural job characteristics (i.e., this category involves the relationships or interactions between the worker and the structural characteristics of the job).

O*NET collects information about these categories by periodically asking workers about these statements/questions, which often have \href{https://www.ONETonline.org/find/descriptor/result/4.C.1.c.2}{unique response categories}. For example, ``How responsible is the worker for work outcomes and results of other workers?'' has response options ranging from \emph{No responsibility} to \emph{Very high responsibility}, while the question, ``How often do you use electronic mail in this job?'' has options ranging from \emph{Never} to \emph{Every day}. We retained O*Net's response scales, several of which were semantically unique across items, but all shared the same 5-point scale. It would likely NOT be considered controversial to referred to these as ``effectively'' Likert-type response scales. Other than minor grammatical editing (for example, changing ``the worker'' to ``you''), we also retained the O*Net wording for our item stems (statements/questions).

@@

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

Data were collected through Prolific, a data collection platform. An email was sent to a random subset of all eligible participants in the Prolific respondent pool, notifying them about their eligibility for the study based on demographic information. Eligibility requirements included being 18+ and holding either a full-time or part-time job. Participants then voluntarily chose to respond to the survey. The survey was conducted online via Qualtrics with an estimated completion time of 40-45 minutes. Participants were asked to think about their primary job while answering the survey, and the items they were presented with depended on the specific job characteristics they initially specified. Thus, if a respondent indicated that a characteristic was not part of their job, they were not subsequently asked to rate the level of resource (i.e., \ldots this aspect of your job is a resource that can be functional in achieving work goals, reduce job demands, or stimulate personal growth/development), challenge (i.e., \ldots this aspect of your job is a challenge that can promote mastery, personal growth, or future gains), or hindrance (i.e., \ldots this aspect of your job is a hindrance that can inhibit personal growth, learning, and work goal attainment) in randomized order. Participants were compensated for their participation in this study in the amount of six dollars through Prolific.

@@

The first hypothesis asks whether job characteristics differ in variability/stability regarding subjective worker perception as a demand or resource. Figure \ref{fig:overallhist} presents frequency distributions standard deviations of characteristic perceptions, grouped by whether that characteristic was rated as a resource, challenge, or demand. As can be seen in the figure, there was a wide range of agreement versus disagreement with resources and challenges, but hindrances were almost universally associated with disagreement (Bartlett's \(K^2\) = 76.83, \emph{p} = 0.00 ).

@@

The second hypothesis stated that job characteristics would not be uniquely categorized as a resource or demand. Table \ref{tab:cortab} provides the correlations among the O*Net item groupings by resource, challenge and hindrance demand. A large proportion of correlations are moderate. Challenge and hindrance demands are smaller in relationship, but mostly negative. Challenge and resource are strongly and positively related. These results provide support for H2 suggesting that there is overlap in how employees perceive job characteristics. Stated another way, job characteristics are not uniquely categorized as a resource or as a demand.

@@

In addition to the two hypotheses, three related research questions were proposed. To answer these research questions, authors first categorized items into the categories listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O*Net item in the autonomy category is, ``How much decision making freedom, without supervision, does your job offer?'' Means for resources, challenges, and hindrances groupings were then computed to explore whether literature-implicated resources and demands were consistently rated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear pattern of high ratings as hindrances for these demands. In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much more variability in how employees rated what should objectively be ``hindrances'' at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. In sum, these results provide some support for RQ 1 and 2.

@@

@@

@@

The major aim and contribution of this paper was to examine whether there was variability in subjective ratings of job characteristics with respect to how much they serve as resources and demands (both challenge and hindrance), and also whether or not there is a match between the literature-implicated resources/demands and subjective ratings of these characteristics using a sample of items from O*Net. The findings broadly revealed that there was relatively more consistency in ratings of resources and challenges characteristics, and far more variability in job characteristics rated as hindrance stressors. This finding lends additional evidence to Horan et al.'s (2020) conclusion that ``\ldots stressors are only challenge or hindrance stressors to the extent that they are perceived as such by employees'' (p.~3). The research questions regarding the match between literature-implicated demand and resource categories and empirical ratings aligns with the consistency/variability we observed in H1. Interestingly, we consistently observed that job characteristics rated as resources were also rated highly as challenge stressors, which are not inherently negative in the way that hindrance stressors are. Lastly, we also found support for the hypothesis that job characteristics are not uniquely categorized as a resource or demand, but rather, some job characteristics are rated highly as both a resource and a demand (H2).

\hypertarget{implications}{%
\subsection{Implications}\label{implications}}

@@

\hypertarget{limitations-and-future-directions}{%
\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}

As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring here. First, we captured only a small number of job characteristics given the nature of our research questions. Because we asked up to four questions about each characteristics, we were limited in the number of job characteristics we could reasonably include. Related to that, we intentionally worked within the O*Net database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources/demands. For example, we included minimal ``social'' resources or interactions with one's supervisor, which the literature would suggest are important resources. Future study should explore this aspect of work. We also used the exact definitions of resource, challenge, and hindrance. It is possible that respondents did not distinguish between the challenge and resource definition as cleanly as we intended and so future research should explore this question differently. It would also be interesting to consider outcomes associated with subjective ratings.
Lastly, there may be some practical utility to pursue training interventions aimed at \emph{how} characteristics are appraised. Perhaps the clinical literature may be informative - for example, within cognitive behavioral therapeutic applications, the way in which situations are appraised can be a mechanism to help battle affective disorders such as depression.{[}\^{}check{]} Given the current findings, where the same characteristic may be viewed similarly as both a demand and resource, it is possible that framing interventions may ameliorate negative outcomes of demands such as, for example, stress or strain.
